%# -*- coding: utf-8-unix -*-
% !TEX program = xelatex
% !TEX root = ../thesis.tex
% !TEX encoding = UTF-8 Unicode
%%==================================================
%% abstract.tex for SJTU Master Thesis
%%==================================================

\begin{abstract}

任务计划和时间管理和每个人的生活和工作都息息相关，
随着社会生活节奏的加快，人们逐渐被各种各样的任务和项目打乱原本的节奏，
无法平衡生活和工作，难以记录自己花费的时间，难以分配自己的精力。
本文主要介绍了一个基于iOS的任务计划和时间管理软件的设计与实现。
该系统旨在通过软件的方式，结合GTD和精力管理的思想，帮助人们规划任务，管理时间和精力。

本系统主要分为今日计划、任务管理、项目管理、精力管理、行为管理五个模块。
今日计划实现对于今天的任务和事件的安排的管理，任务管理通过对任务进行详尽的设置和项目分类，对任务进一步细化，
项目管理对任务之间的依赖关系进行处理和安排，精力管理可以展示用户对于每个任务花费的精力，行为管理是任务管理的进一步细化，
对用户的行为进行记录，并进行展示。

本系统采用Swift 5语言开发，使用方便，界面友好，能够帮助用户合理规划和安排时间。


\end{abstract}

\begin{englishabstract}

Mission planning and time management are closely related to everyone’s life and work.
As the pace of social life accelerates, people are gradually disrupted by the various tasks and projects.
Unable to balance life and work, it is difficult to record the time spent, and it is difficult to allocate your energy.
This paper mainly introduces the design and implementation of an iOS-based task plan and time management software.
The system is designed to help people plan tasks and manage time and effort through software, combined with GTD and energy management ideas.

The system is mainly divided into five modules: planning, task management, project management, energy management and behavior management.
Today plans to manage the scheduling of today's tasks and events. Task management further refines the tasks by detailed setting and classification of tasks.
Project management processes and arranges the dependencies between tasks. Energy management can show the user's energy spent on each task. Behavior management is a further refinement of task management.
Record and display the user's behavior.

This system is developed in Swift 5 language. It is easy to use and friendly. It can help users plan and schedule time reasonably.

\end{englishabstract}

